---
title: "Example meta-analysis dataset"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

The purpose of this webinar is to explore how data visualisation can be deployed to find "insights" when faced with a [*big data*](https://raw.githubusercontent.com/VIS-SIG/Wonderful-Wednesdays/dec/data/2020/2020-11-11/BIG_DATA_PSI_WW_DEC2020.csv). 

For this webinar, we introduce the challenge of working with pooled clinical trials. This is often referred to as meta-analysis. 

Key issues where data visualisation can help are around the investigation of whether studies can be combined due to study heterogeneity among individual studies. This throws up questions such as:

* What graphical tools can be used to assess heterogeneity, describing the fixed and random-effects? 
* what variables are potentially prognostic or predictive of outcome, etc. 
* where can graphical methods provide some general recommendations?


## Background

Meta-analysis are a popular approach for summarising a large number of clinical trials. We can resolving discrepancies raised by individual these trials, identify new "insights", or attempt to tackle new research questions.  

The example simulated data set is based on seven phase III studies in Hypertension. The objective of the studies were to compare the use of intensive hypertensive medicences compared to standard of care to control blood pressure. The studies are inspired by the large blood pressure intervention studies such as [SPRINT](https://biolincc.nhlbi.nih.gov/studies/sprint/). In this case, instead of a large single trial, we are faced with an integreted set of seven seperate trials.  


## Data set

The data set is an abridged version of [CDISC ADaM](https://www.cdisc.org/standards/foundational/adam). 

The data set contains the following key variables for analysis: 

* **STUDYID**	Masked study identifer	
* **USUBJD**	Masked subject identifier	Identifer
* **TRT01P**	Randomised treatment
* **AVAL**	Mean systolic blood pressure (mm Hg) measured at 1-year
* **BASE**  Mean systolic blood pressure (mm Hg) measured at baseline
* **CHG**	 Change from baseline mean systolic blood pressure (SBP) [mm Hg] at 1-year	
* **PCHG**	Percentage change from baseline mean systolic blood pressure (%change) at 1-year
* **AVALCAT1**	Responder analysis - patients with controlled SBP at 1-Year (<=120 mmHg) 1 = Yes, 0 = No	1-Year

A wide collection of baseline measurements are also included which can be explored to for subgroups or differential treatment effects. For a detailed overview of the data set, please refer to the **data dictionary** section below (or in the file that can be downloaded [here](DataDictionaryDec2020.xlsx)).

## Data Dictionary {#dict}

In this section is a description of all variables. 


| Variable   name | Description | Assessment Visit |
|-|-|-|
| STUDYID | Masked study identifer | Identifer |
| USUBJD | Masked subject identifier | Identifer |
| TRT01P | Randomised treatment | Treatment |
| TRT01PC | Randomised treatment (Character) | Treatment |
| TRT01PN | Randomised treatment (Numeric) | Treatment |
| PARAM | Analysis variable label | 1-Year |
| AVAL | Mean systolic blood pressure (mm   Hg) measured at 1-Year | 1-Year |
| CHG | Change from baseline Mean   systolic blood pressure (mm Hg) | 1-Year |
| PCHG | Percentage change from baseline   Mean systolic blood pressure (%change) | 1-Year |
| AVALCAT1 | Responder analysis - patients   with controlled SBP at 1-Year (<=120 mmHg) 1 = Yes, 0 = No | 1-Year |
| AVALCAT1N | Responder analysis - patients   with controlled SBP at 1-Year (<=120 mmHg) 1 = Yes, 0 = No | 1-Year |
| AVALCAT2 | Mean systolic blood pressure (mm   Hg) measured at 1-Year categories (<= 132, 132 - 145, >= 145) | 1-Year |
| AVALCAT2N | Mean systolic blood pressure (mm   Hg) measured at 1-Year categories (numeric)    (<= 132, 132 - 145, >= 145) | 1-Year |
| AGE | Age (years) | Baseline |
| AGECAT1 | Age Group 3: 75 years and older   = TRUE | Baseline |
| AGECAT1C | Age Group 3: 75 years and older   = TRUE | Baseline |
| AGECAT1N | Age Group 3: 75 years and older   = TRUE | Baseline |
| ALBSI | Albumin (g/L) | Baseline |
| BASE | Mean systolic blood pressure (mm   Hg) measured at baseline | Baseline |
| BASOSI | Basophils (Absolute) (10E9/L) | Baseline |
| BICARSI | Bicarbonate (mmol/L) | Baseline |
| BILISI | Bilirubin (umol/L) | Baseline |
| BMI | BMI | Baseline |
| BUNSI | Blood Urea Nitrogen (mmol/L) | Baseline |
| CASI | Calcium (mmol/L) | Baseline |
| CHD10R1 | 10-year Coronary heart disease   (CHD) risk category (High (>20%) , Medium (10-20%), Low (<10%)) | Baseline |
| CHD10R1N | 10-year CHD risk category   (Numeric, 1 = Low, 2 = Medium, 3 = High) | Baseline |
| CHOL_HDL | Ratio of Total Cholesterol / HDL | Baseline |
| CHOLSI | Cholesterol (mmol/L) | Baseline |
| COUNTRY | Country indicator | Baseline |
| CREATSI | Creatinine (umol/L) | Baseline |
| EOSLESI | Eosinophils/Leukocytes (%) | Baseline |
| EOSSI | Eosinophils (Absolute) (10E9/L) | Baseline |
| ETHNIC | Ethnicity | Baseline |
| GGTSI | Gamma Glutamyl Transferase (U/L) | Baseline |
| GLUCPSI | Glucose, Plasma, Fasting   (mmol/L) | Baseline |
| GREGGR1O | Regional stratification group | Baseline |
| HCT | Hematocrit | Baseline |
| HDLSI | HDL Cholesterol (mmol/L) | Baseline |
| HDT | Phosphate (mmol/L) | Baseline |
| HEIGHT | Height (cm) | Baseline |
| HGBSI | Hemoglobin (g/L) | Baseline |
| KSI | Potassium (mmol/L) | Baseline |
| LDLSI | LDL Cholesterol (Assayed)   (mmol/L) | Baseline |
| LPASI | Lipoprotein-A Protein (g/L) | Baseline |
| LYMLESI | Lymphocytes/Leukocytes (%) | Baseline |
| LYMSI | Lymphocytes (Absolute) (10E9/L) | Baseline |
| MONOLSI | Monocytes/Leukocytes (%) | Baseline |
| RACE | Race | Baseline |
| SBPCAT1C | Mean systolic blood pressure (mm   Hg) at baseline (Category) | Baseline |
| SBPCAT1N | Mean systolic blood pressure (mm   Hg) at baseline (Numeric) | Baseline |
| SEX | Sex | Baseline |
| TRIGFSI | Triglycerides (Fasting) (mmol/L) | Baseline |
| URATESI | Uric Acid (umol/L) | Baseline |
| WBCSI | Leukocytes (10E9/L) | Baseline |
| WEIGHT | Weight (kg) | Baseline |


### Downloading data 

**NOTE** to download a single data set as a csv file, click on the raw
button and save the [file](https://raw.githubusercontent.com/VIS-SIG/Wonderful-Wednesdays/dec/data/2020/2020-11-11/BIG_DATA_PSI_WW_DEC2020.csv). The [following link describes the process in
further
detail](https://stackoverflow.com/questions/4604663/download-single-files-from-github).



## Example analysis

This section illustrates a simple example analysis. 

### Load data

```{r, warning=FALSE, message=FALSE}
library(tidyverse)    
library(broom)
data <- read_csv("BIG_DATA_PSI_WW_DEC2020.csv")
```

### Plot pooled data

Plot the pre-post mean systolic blood pressure of all patients for all studies. 

```{r, warning=FALSE, message=FALSE}
data %>% ggplot(aes(x = BASE, y = AVAL)) +
  geom_point()
```

### Simple analysis by study

A between study comparison of intensive treatment vs standard of care. 

```{r, warning=FALSE, message=FALSE}
data %>% 
  group_by(STUDYID) %>%
  do(fit = tidy(lm(AVAL ~ BASE + TRT01PN, data = .))) %>% 
  unnest(fit) %>%
  filter(term == "TRT01PN")
```

Across all studies, there is evidence to suggest intensive treatment improves blood pressure control (decreases blood pressure) at 1-year compared to standard of care. 


